Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 discussion.tex
...

  -   Supporting situations where the API is deployed across multiple containers for example.

@@

  \subsection*{Advanced Outlier Analysis}

    - We need more advanced outlier analysis tools... Instead of manually searching in the page to build stats about Google vs. Microsoft

    - outlier detection and monitoring is important. manual exploration is critical. however, one needs a performant way of analyzing multiple logs. in the example we saw we had to use the search facility to investigate our hypothesis that Google Translate was slower than Microsoft Translate. Moreover, these trends might change too...

>>>>

  -   Supporting situations where the API is deployed across multiple containers for example.
  \ml{@V: Do you want to add this? Or can we skip it?}

@@

    \ml{@V: do you want to give a first stab to this?}

  % \subsection*{Advanced Outlier Analysis}

  %   - We need more advanced outlier analysis tools... Instead of manually searching in the page to build stats about Google vs. Microsoft

  %   - outlier detection and monitoring is important. manual exploration is critical. however, one needs a performant way of analyzing multiple logs. in the example we saw we had to use the search facility to investigate our hypothesis that Google Translate was slower than Microsoft Translate. Moreover, these trends might change too...
